### 2016-05-31 papers/thesis-vischer/Thesis.tex
fix an annoying line break with Brenden

\begin{algorithm}[!b]
\caption{Thermodynamic integration.}
\label{alg:ti}
\begin{alg}
\item Construct cell with desired number of spheres with filling fraction of zero.
\item Move spheres random fractions of a predefined translation distance. \label{alg-ti-move}
\item Repeat step \ref{alg-ti-move} for desired number of iterations before checking the small cell.
\item Check the ``small cell'' by shrinking the volume and determine whether or not the configuration is still valid.
\item If configuration is still valid, increment the count of valid checks.
\item If configuration is invalid, increment the count of failed checks. \label{alg-ti-move-end}
\item Repeat steps \ref{alg-ti-move} - \ref{alg-ti-move-end} until desired iterations reached.

@@

\subsection{Data Storage}
All simulation output is saved in text files for plotting and visualization ease. The question of organization becomes important with this amount of files being generated. Each different system simulation (length $L = \sqrt2 \sigma, 5,10$) has data regarding each doubling regime ($i=0,1, 2, 3$) and each doubling regime contains data for each possible sphere count ($N=1, 2, 3\dots N_{max}$, where $N_{max}$ is typically limited by maximal sphere packing of $N_{max}V_{\text{sphere}}/L^3\approx.741$). The file structure mirrors the above symmetry: 
\begin{align*}
                &\rightarrow \text{i=0} &\rightarrow \text{N=0}\\
                & &\rightarrow \text{N=1}\\
                && \vdots\\
\text{System} & \rightarrow \text{i=1} &\rightarrow \text{N=0}\\
                && \rightarrow \text{N=1}\\
                &&\vdots\\
                &\rightarrow \text{i=2} &\rightarrow \text{N=0}\\
                && \rightarrow \text{N=1}\\
                &&\vdots\\
\end{align*}
Each sphere count subfolder contains a single text file from TMMC output and another subfolder where all of the thermodynamic integration output is stored. Each thermodynamic integration simulation outputs a single text file upon completion of each filling fraction step. On average, a single calculation requires approximately $175$ steps. This structure was chosen both for elegant parallelism and for plotting accessibility.

>>>>

\begin{algorithm}
\caption{Thermodynamic integration.}
\label{alg:ti}
\begin{alg}
\item Construct cell with desired number of spheres with filling fraction of zero.
\item Move spheres random fractions of a predefined translation distance. \label{alg-ti-move}
\item Repeat step \ref{alg-ti-move} for desired number of iterations before checking the small cell.
\item Check the ``small cell'' by shrinking the volume and determine whether or not the configuration is still valid.
\item If configuration is still valid, increment the count of valid checks.
\item If configuration is invalid, increment the count of failed checks. \label{alg-ti-move-end}
\item Repeat steps \ref{alg-ti-move} - \ref{alg-ti-move-end} until desired iterations reached.

@@

\subsection{Data Storage}
All simulation output is saved in text files for plotting and visualization ease. The question of organization becomes important with this amount of files being generated. Each different system simulation (length $L = \sqrt2 \sigma, 5,10$) has data regarding each doubling regime ($i=\nobreak 0,1, 2, 3$) and each doubling regime contains data for each and every possible sphere count $N=\nobreak 1, 2, 3\dots N_{max}$, where $N_{max}$ is typically limited by maximal sphere packing of $N_{max}V_{\text{sphere}}/L^3\approx\nobreak 0.741$. The file structure mirrors the above symmetry:
\begin{align*}
                &\rightarrow \text{i=0} &\rightarrow \text{N=0}\\
                & &\rightarrow \text{N=1}\\
                && \vdots\\
\text{System} & \rightarrow \text{i=1} &\rightarrow \text{N=0}\\
                && \rightarrow \text{N=1}\\
                &&\vdots\\
                &\rightarrow \text{i=2} &\rightarrow \text{N=0}\\
                && \rightarrow \text{N=1}\\
                &&\vdots\\
\end{align*}
Each sphere count subfolder contains a single text file from TMMC output and another subfolder where all of the thermodynamic integration output is stored. Each thermodynamic integration simulation outputs a single text file upon completion of each filling fraction step. On average, a single calculation requires approximately $175$ steps. This structure was chosen both for elegant parallelism and for plotting accessibility.
